Assessing rigor and impact of research software for hiring and promotion in psychology: A comment on Gärtner et al.~(2022)

### 2023-10-04 manuscript.Rmd
add School of Cognition affiliation

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, MSB Medical School Berlin, Berlin, Germany"
  - id            : "2"
    institution   : "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
  - id            : "3"
    institution   : "Max Planck UCL Centre for Computational Psychiatry and Ageing Research, Berlin, Germany"
  - id            : "4"
    institution   : "Department of Psychology, Humboldt-Universität zu Berlin, Berlin, Germany"

>>>>

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, MSB Medical School Berlin, Berlin, Germany"
  - id            : "2"
    institution   : "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
  - id            : "3"
    institution   : "Max Planck UCL Centre for Computational Psychiatry and Ageing Research, Berlin, Germany"
  - id            : "4"
    institution   : "Max Planck School of Cognition, Leipzig, Germany"
